Pillar 1 - Student Topic Profile

### 2019-04-30 Pillar 1 - Topic Profile.Rmd
correct topic model input file

```{r load, cache.lazy = TRUE}
#load("App/Recommender System/topic_model_gb.RDATA")
load("App/Recommender System/data_topic_models.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/course_current.RDATA")

>>>>

```{r load, cache.lazy = TRUE}
load("App/Recommender System/app_model.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/course_current.RDATA")
